### 2016-11-14 ms/ms.tex
Marilia changed the ms accoring to some of Paulinhas suggestions

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations.%  In contrast, the
  % non-assembling networks did not restructure as frequently.
  % Across all communities, pollinator species were opportunistic in the
  % flowers they visited.
  The most persistent and generalized species
  were also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. % High
  % species and interaction turnover was ubiquitous across assembling
  % and non-assembling communities, though unique interactions turned
  % over at higher rates in assembling hedgerows as the networks
  % continually reorganized.
  % Nestedness of assembling networks also increased through time, but
  The sensitivity of networks to cascading perturbations,
  increased with assembly, at least partially due to accumulating
  species richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration --- challenging
  the widely-held hypothesis that mutualistic networks assemble
  through preferential attachment.
\end{abstract}

@@

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that phenologically new plant and pollinator species tended to
interact with already well-connected species, potentially because
these species are either more abundant or more temporally
persistent. In addition, using a space-for-time substitution to study
primary succession along a glacier foreland, \cite{albrecht2010plant}
also found some evidence that assembly occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}.  An
increase in nestedness could result from the preferential attachment
process where specialist species attach to the well-connected,
generalist core.

@@

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, devoto2012understanding}, suggesting
interactions are changing as the community develops. Understanding the
mechanisms of network assembly will help to guide community
restoration. Facilitating network restoration is especially imperative
in areas where species interactions provide essential ecosystem
services, such as crop pollination. To ensure the continued provision
of ecosystem services and curb biodiversity loss, it is critical to
restore pollinators and their interactions in agricultural
landscapes. To promote pollinator services in agriculture, farmers may
chose to plant strips of native plants along farm edges (hedgerows) to
help provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, kremen-2015-602, ponisio2015farm}, and
promote the persistence and colonization of floral resource
specialists \citep{mgonigle-2015-x}. It is important to understand how
these new species are being incorporated into the network as the
community assembles, and the consequences for interaction patterns and
robustness.

@@

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness.
% (Gaiarsa et al., in prep)
Algebraic connectivity relates to how difficult it is to turn a
network into completely disconnected groups of species
\citep{costa2007characterization, gibert2013spatial}. The larger the
algebraic connectivity, the more sensitive a network is to cascading
perturbations. Perturbations, such as the decrease in abundance of a
plant or pollinator, can have negative consequences for the species in
the network. For example, a decrease in abundance of a pollinator will
diminish the pollination services it provides to plants. The affected
plants would set less seeds, and decrease in abundance the subsequent
year. Consequently, other pollinators that depended on those plant
species would also be affected, and the effects of this perturbation
would continue to propagate throughout the network. Alternatively,
perturbations could also have a positive effect. For example, the
increase in abundance of a plant species would lead to an increase in
resource availability for the pollinators. The examples of negative
perturbations (e.g., resource collapse, disease spreading, parasites),
however, outnumber possible positive perturbations. It is important to
note that both robustness and algebraic connectivity assume that the
network is static. They do not account for the ability of species to
alter their interaction depending on circumstances and the resource
availability.

@@

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species were removed incrementally by
degree % (estimate
% of the slope of robustness through time $\pm$ SE, $6*10^{-5} \pm
% 4*10^{-3}$, $p$-value=$0.987$)
or abundance. % ($0.001 \pm 0.003$,
% $p$-value=$0.65$)
In contrast, the sensitivity of networks to
cascading perturbations, as measured by the algebraic connectivity of
the network, increased as the network assembled (Fig.~\ref{fig:rob},
estimate of the slope of sensitivity to cascading perturbations
through time $\pm$ SE, $0.6814 \pm 0.272$, $p$-value=$0.042$).

@@

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what would be expected from preferential
attachment. With a preferential attachment process, we expect that the
most persistent and high degree species would remain stable in the
network core during assembly
\citep{barabasi1999emergence}. Surprisingly, however, we encountered
the opposite pattern. For example, the four most ubiquitous species in
our study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
which module they were a member in across years in all the assembling
hedgerows. Because species degree and persistence were strongly
correlated, it is difficult to disentangle the causal mechanism for
why species with those characteristics are so variable in their
network position. Generalized species may be better able to exploit
the limited floral resources in the intensively managed agriculture
landscape, and thus also be the most persistent \citep[in ant-plant
mutualisms, ][]{diaz2010changes}. More persistent species usually have
longer phenologies, so they can visit many different flowers,
resulting in a higher degree \citep{Vazquez2009,
  fort2016abundance}. Either way, our result suggests that adaptable
species can change their network position to utilize the most
advantageous floral resources available, which may depend on both the
other pollinator species that are present and the state of the plant
community \citep{macleod2016measuring, gomez2006ecological,
  Waser1996}. Thus given the opportunity and ability to
use different resources, species will often change their network
positions \citep{macleod2016measuring}.

@@

Interestingly, however, the changes in network patterns associated
with assembly did not effect the robustness of hedgerow communities to
species loss. This is particularly surprising given the observed
increase in nestedness, which is often associated with an enhanced in
robustness to extinction \citep{Memmott2004}. Perhaps assembling
hedgerows have yet to reach sufficient levels of nestedness to realize
the benefits nestedness confers. Nestedness of the assembling
hedgerows, however, did not asymptote within the eight years following
restoration that the sites were surveyed, so hedgerow networks may
eventually reach sufficient levels of nestedness to gain the
robustness advantage.

Contrary to the general restoration goals, the susceptibility of the
networks to cascading perturbations increased as the communities
assembled. Because network vulnerability to cascading perturbations,
as measured by algebraic connectivity, is correlated with species
richness, the increase in and plant and pollinator richness following
restoration is at least partially responsible for the increase in
response to cascading effects. Connectance is also positively related
to algebraic connectivity \citep{gibert2013spatial}, but because we
observed a decrease in connectance, topological characteristics of the
networks beyond species richness and connectance are needed to explain
the increased sensitivity to perturbations spreading. These hedgerows
were designed to provide floral resources to the largest number of
pollinators across the growing season \citep{menz-2010-4}. The
generalized nature of the floral community may explain why the
networks tended to be more generalized than expected if interactions
were randomly distributed across species (Fig.~\ref{fig:baci}). In
addition, the design of the hedgerow plantings may have facilitated
the emergence of a single, highly connected module in all of the
networks (see \ref{fig:changePoints2} for examples). This network
configuration results in short path lengths (the distance between
species in a network based on their shared partners), and thus, a
perturbation in one species can more easily spread to other
species. In order to promote more resilient communities, future
restoration efforts should explore designing floral communities to
promote more interaction partitioning using, for example, algorithms
to optimize different network properties based on prior knowledge of
pollinator floral preferences \citep{mgonigle2016tool}, and on desired
network architectures that renders them more robust both to species
loss and to cascading effects.

@@

We would like to thank Paulo R.~Guimar{\~a}es Jr., Aaron Clauset and
Matthew Hutchinson for their invaluable discussions and comments, and
Leto Peel for help with the change point analysis.  We thank the
growers and land owners that allowed us to work on their property. We
also greatly appreciate the identification assistance of expert
taxonomists Martin Hauser, Robbin Thorp and Jason Gibbs.  This work
was supported by funding from the Army Research Office
(W911NF-11-1-0361 to CK), the Natural Resources Conservation Service
(CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship, the USDA
NIFA Graduate Fellowship, and the Berkeley Institute for Data
Science. Funding for MPG was provided by S{\~a}o Paulo Research
Foundation (FAPESP, grant 2013/13319-5). We also appreciate the Santa
Fe Institute for facilitating this international collaboration.

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/changePoint/plotting/networksv1.pdf}
  \caption{Assembling hedgerow networks had more changing points
    (vertical red lines) than non-assembling hedgerows and weedy field
    margins (a representative sample of non-assembling sites are
    depicted here). In each network, plants and pollinators are
    represented by green and yellow circles, respectively, weighted by
    their degree. Each species has a consistent position in the
    perimeter of the network across years. In the assembling
    hedgerows, colored squares in the corner of each network represent
    the year of assembly. Asterisks indicate the year the hegdgerow
    was planted. Before that, the sites were weedy field margins.}
  \label{fig:changePoints}
\end{figure}
\clearpage

\begin{sidewaysfigure}
  \centering
  \includegraphics[width=.95\textwidth]{../analysis/changePoint/plotting/communitiesSkanky3.pdf}
  \caption{The module membership between network changing points. Two
    representative assembling hedgerows are depicted. In the top
    panel, species are grouped by module. The bottom panels visualize
    the flow of species between modules between changing points. }
  \label{fig:changePoints2}
\end{sidewaysfigure}
\clearpage

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/variability/figures/turnover_panels.pdf}
  \caption{The species, interaction and weighted interactions turnover
    of plant-pollinator networks at non-assembling field margins
    sites, assembling hedgerows, and non-assembling, mature
    hedgerows. Rates of species and interaction turnover were similar
    between site types, though mature hedgerows has marginally
    significantly less pollinator turnover.  However, when
    interactions where weighted by their similarity, both hedgerow
    types had higher turnover that unrestored field margins. Boxplots
    represent medians (black horizontal line) first and third
    quartiles (box perimeter) and extremes (whiskers). }
  \label{fig:beta}
\end{figure}
\clearpage

>>>>

\begin{abstract}  
 % The ability of communities to maintain function in the face of
  %species extinction is related to the structure of networks. Lauren - i changed the phrasing because structure of network and network structure were too close.
  The structure of interaction networks is related to the ability of communities to maintain function in the face of
  species extinction. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations.%  In contrast, the
  % non-assembling networks did not restructure as frequently.
  % Across all communities, pollinator species were opportunistic in the
  % flowers they visited.
   Generalist species were the most persistent and 
also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. % High
  % species and interaction turnover was ubiquitous across assembling
  % and non-assembling communities, though unique interactions turned
  % over at higher rates in assembling hedgerows as the networks
  % continually reorganized.
  % Nestedness of assembling networks also increased through time, but
  The sensitivity of networks to cascading perturbations,
  increased with assembly, at least partially due to accumulating
  species richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration --- challenging
  the widely-held hypothesis that mutualistic networks assemble
  through preferential attachment.
\end{abstract}

@@

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[the "rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that phenologically new plant and pollinator species tended to
interact with already well-connected species, potentially because
these species are either more abundant or more temporally
persistent. In addition, using a space-for-time substitution to study
primary succession along a glacier foreland, \cite{albrecht2010plant}
also found some evidence that assembly occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}.  An
increase in nestedness could result from the preferential attachment
process where specialist species attach to the well-connected,
generalist core.

@@

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially "applied succession"
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, devoto2012understanding}, suggesting
interactions are changing as the community develops. Understanding the
mechanisms of network assembly will help to guide community
restoration. Facilitating network restoration is especially imperative
in areas where species interactions provide essential ecosystem
services, such as crop pollination. To ensure the continued provision
of ecosystem services and curb biodiversity loss, it is critical to
restore pollinators and their interactions in agricultural
landscapes. To promote pollinator services in agriculture, farmers may
chose to plant strips of native plants along farm edges (hedgerows) to
help provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, kremen-2015-602, ponisio2015farm}, and
promote the persistence and colonization of floral resource
specialists \citep{mgonigle-2015-x}. It is important to understand how
these new species are being incorporated into the network as the
community assembles, and the consequences for interaction patterns and
robustness.

@@

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness.
% (Gaiarsa et al., in prep)
Algebraic connectivity relates to how difficult it is to turn a
network into completely disconnected groups of species
\citep{costa2007characterization, gibert2013spatial}. The larger the
algebraic connectivity, the more sensitive a network is to cascading
perturbations. Perturbations, such as the decrease in abundance of a
plant or pollinator, can have negative consequences for the species in
the network. For example, a decrease in abundance of a pollinator will
diminish the pollination services it provides to plants. The affected
plants would set less seeds, and decrease in abundance the subsequent
year. Consequently, other pollinators that depended on those plant
species would also be affected, and the effects of this perturbation
would continue to propagate throughout the network. Alternatively,
perturbations could also have a positive effect if, for example, the
increase in the abundance of a plant species lead to an increase in
resource availability for pollinators. The examples of negative
perturbations (e.g., resource collapse, disease spreading, parasites),
however, outnumber possible positive perturbations. It is important to
note that both robustness and algebraic connectivity assume that the
network is static. They do not account for the ability of species to
alter their interaction depending on circumstances and the resource
availability.

@@

\subsection*{Network robustness}
Assembly did not affect network robustness to species
extinction when species were removed incrementally by
degree % (estimate
% of the slope of robustness through time $\pm$ SE, $6*10^{-5} \pm
% 4*10^{-3}$, $p$-value=$0.987$)
or abundance. % ($0.001 \pm 0.003$,
% $p$-value=$0.65$)
In contrast, the sensitivity of networks to
cascading perturbations, as measured by the algebraic connectivity of
the network, increased as the network assembled (Fig.~\ref{fig:rob},
estimate of the slope of sensitivity to cascading perturbations
through time $\pm$ SE, $0.6814 \pm 0.272$, $p$-value=$0.042$).

@@

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what would be expected from preferential
attachment. In a preferential attachment process, we expect that the
most persistent and high degree species would remain stable in the
network core during assembly
\citep{barabasi1999emergence}. Surprisingly, however, we encountered
the opposite pattern. For example, the four most ubiquitous species in
our study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
which module they were a member in across years in all the assembling
hedgerows. Because species degree and persistence were strongly
correlated, it is difficult to disentangle the causal mechanism for
why species with those characteristics are so variable in their
network position. Generalized species may be better able to exploit
the limited floral resources in the intensively managed agriculture
landscape, and thus also be the most persistent \citep[in ant-plant
mutualisms, ][]{diaz2010changes}. More persistent species usually have
longer phenologies, so they can visit many different flowers,
resulting in a higher degree \citep{Vazquez2009,
  fort2016abundance}. Either way, our result suggests that adaptable
species can change their network position to utilize the most
advantageous floral resources available, which may depend on both the
other pollinator species that are present and the state of the plant
community \citep{macleod2016measuring, gomez2006ecological,
  Waser1996}. Thus given the opportunity and ability to
use different resources, species will often change their network
positions \citep{macleod2016measuring}.

@@

Interestingly, however, the changes in network patterns associated
with assembly did not affect the robustness of hedgerow communities to
species loss. This is particularly surprising given the observed
increase in nestedness, which is often associated with an increase in
robustness to extinction \citep{Memmott2004}. Perhaps assembling
hedgerows have yet to reach sufficient levels of nestedness to realize
the benefits nestedness confers. Nestedness of the assembling
hedgerows, however, did not asymptote within the eight years following
restoration that the sites were surveyed, so hedgerow networks may
eventually reach sufficient levels of nestedness to gain the
robustness advantage.

%Lauren - I changed the first part  of this paragraph but I really don't thinks it is that confusing. The problem is that it is indeed very theoretical, but it is impossible to make our point without being too technical.. I tried to decrease the use of jargons.
Contrary to the general restoration goals, networks' susceptibility 
 to cascading perturbations increased as the communities assembled. We measured vulnerability to cascading perturbations as the algebraic connectivity of the network: the greater the algebraic connectivity, the harder it  is to turn a network into completely disconnected groups of species, and the more vulnerable a community is to cascading perturbations. However, algebraic connectivity is positively related not only to the number of species--- species richness--- but also to the number of interactions in the network--- connectance \citep{gibert2013spatial}. Therefore, the increase in and plant and pollinator richness following
restoration is at least partially responsible for the increase in
response to cascading effects. Additionally, despite the correlation between connectance and algebraic connectivity \citep{gibert2013spatial}, we
observed a decrease in connectance. Thus, topological characteristics of the
networks beyond species richness and connectance are needed to explain
the increased sensitivity to perturbations spreading. These hedgerows
were designed to provide floral resources to the largest number of
pollinators across the growing season \citep{menz-2010-4}. The
generalized nature of the floral community may explain why the
networks tended to be more generalized than expected if interactions
were randomly distributed across species (Fig.~\ref{fig:baci}). In
addition, the design of the hedgerow plantings may have facilitated
the emergence of a single, highly connected module in all of the
networks (see \ref{fig:changePoints2} for examples). This network
configuration results in short path lengths (the distance between
species in a network based on their shared partners), and thus, a
perturbation in one species can more easily spread to other
species. In order to promote more resilient communities, future
restoration efforts should explore designing floral communities to
promote more interaction partitioning using, for example, algorithms
to optimize different network properties based on prior knowledge of
pollinator floral preferences \citep{mgonigle2016tool}, and on desired
network architectures that renders them more robust both to species
loss and to cascading effects.

@@

We would like to thank Paulo R.~Guimar{\~a}es Jr., Aaron Clauset,
Matthew Hutchinson and Ana Paula A. Assis for their invaluable discussions and comments, and
Leto Peel for help with the change point analysis.  We thank the
growers and land owners that allowed us to work on their property. We
also greatly appreciate the identification assistance of expert
taxonomists Martin Hauser, Robbin Thorp and Jason Gibbs.  This work
was supported by funding from the Army Research Office
(W911NF-11-1-0361 to CK), the Natural Resources Conservation Service
(CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship, the USDA
NIFA Graduate Fellowship, and the Berkeley Institute for Data
Science. Funding for MPG was provided by S{\~a}o Paulo Research
Foundation (FAPESP, grant 2013/13319-5). We also appreciate the Santa
Fe Institute for facilitating this international collaboration.

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/changePoint/plotting/networksv1.pdf}
  \caption{Assembling hedgerow networks had more changing points
    (vertical red lines) than non-assembling hedgerows and weedy field
    margins (a representative sample of non-assembling sites are
    depicted here). In each network, plants and pollinators are
    represented by green and yellow circles, respectively, weighted by
    their degree. Each species has a consistent position in the
    perimeter of the network across years. Asterisks indicate the year the hegdgerow
    was planted. Before that, the sites were weedy field margins.}
  \label{fig:changePoints}
\end{figure}
\clearpage

\begin{sidewaysfigure}
  \centering
  \includegraphics[width=.95\textwidth]{../analysis/changePoint/plotting/communitiesSkanky3.pdf}
  \caption{The species module membership between network changing points. Two
    representative assembling hedgerows are depicted. In the top
    panel, species are grouped by module. The bottom panels visualize
    the flow of species between modules between changing points. Each line represents the change of s species from one module to another. }
  \label{fig:changePoints2}
\end{sidewaysfigure}
\clearpage

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/variability/figures/turnover_panels.pdf}
  \caption{Species interaction and weighted interactions turnover
    of plant-pollinator networks at non-assembling field margins
    sites, assembling hedgerows, and non-assembling, mature
    hedgerows. Rates of species and interaction turnover were similar
    between site types, though mature hedgerows has marginally
    significantly less pollinator turnover.  However, when
    interactions were weighted by their similarity, both hedgerow
    types had higher turnover than unrestored field margins. Boxplots
    represent medians (black horizontal line) first and third
    quartiles (box perimeter) and extremes (whiskers). }
  \label{fig:beta}
\end{figure}
\clearpage
